Development of Physics or HPC Optimisation of a parallel 2D lattice Boltzmann solver using GPUs/CUDA

### 2017-08-11 Thesis/Draft.tex
up

\section{Performance of the parallel code}\label{sec:performance}
\subsection{2D model}
\subsubsection{Normal distribution function v1.0}
\subsubsection{Enhanced distribution function v2.0}
\subsubsection{Optimizations v2.1}
\subsubsection{Loop unrolling v2.2}
\subsubsection{Final version v2.3}
\subsubsection{High order color gradient}
\subsubsection{CUDA compute capability}
\subsection{3D model}
\subsubsection{Enhanced distribution function v1.0}
\subsubsection{Final version v1.1}
\subsubsection{High order color gradient}
\subsubsection{CUDA compute capability}
\subsection{Hardware}
\subsection{Double vs Single}
\chapter{Conclusions}

>>>>

\section{Performance of the parallel code}\label{sec:performance}
In this section, we will analyze and discuss the performance obtained throughout the various stages of development of the code. We will first compare optimizations techniques employed, followed by the usage of different code and compiler features. We will then compare the different hardware used and finally the impact in performance between using double and single precision. 
\subsection{GPU specification}
To perform the tests, we first need the hardware on which to perform the tests on. Since we are using CUDA, we must obviously use machines with NVIDIA GPUs. Table \ref{tab:specs} shows the specification of the characteristics of each machine's GPU. GRID and Delta are a part of Cranfield's HPC center, while the laptop is my own personal laptop with a less powerful GPU.
\begin{table}[H]
	\centering
	\begin{tabular}{|l|c|c|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{}} & \textbf{GRID} & \textbf{Delta} & \textbf{Personal laptop} \\ \hline
		\textbf{GPU}                    & Tesla K40m    & Tesla K80      & GeForce GTX 850M         \\ \hline
		\textbf{Memory}                 & 12288 MB      & 11440 MB       & 4044 MB                  \\ \hline
		\textbf{CUDA capability}        & 3.5           & 3.7            & 5.0                       \\ \hline
		\textbf{CUDA cores}             & 2880          & 2496           & 640                      \\ \hline
		\textbf{GPU clock rate}         & 745 MHz       & 824 MHz        & 902 MHz                  \\ \hline
		\textbf{Mem. clock rate}        & 3004 MHz      & 2505 MHz       & 1001 MHz                 \\ \hline
	\end{tabular}
	\caption{Specification of the used GPUs}
	\label{tab:specs}
\end{table}
\subsection{2D model}
\subsubsection{Normal distribution function v1.0}
\subsubsection{Enhanced distribution function v2.0}
\subsubsection{Optimizations v2.1}
\subsubsection{Loop unrolling v2.2}
\subsubsection{Final version v2.3}
\subsubsection{High order color gradient}
\subsubsection{CUDA compute capability}
\subsection{3D model}
\subsubsection{Enhanced distribution function v1.0}
\subsubsection{Final version v1.1}
\subsubsection{High order color gradient}
\subsubsection{CUDA compute capability}
\subsection{Hardware}
\subsection{Double vs Single}
\chapter{Conclusions}
